Meta RL analyses

### 2019-05-20 meta_RL_analyses.Rmd
Comparing different methods of performing a new task -- why is meta-mapping useful?

  p = ggplot(data, aes_string(x=x_var, y=y_var, color=color_var)) +  
    geom_hline(yintercept=0., linetype=2, alpha=0.5) +
    geom_point(stat="summary", fun.y=mean, size=2) +
    scale_color_manual(values=c("#555093", "#f38f22"))

@@

```{r}
summary_plot(language_d %>%
               filter(epoch == 0),
             "game_type", "reward", "is_new_game",
             optimal_baselines) +
  facet_wrap(. ~ named_run_type) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#ggsave("writing/figures/language_basic.png", width=5, height=3.5)
#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/crappy_language.png", width=5, height=3)
```

@@

meta_d = meta_d %>%
  filter(epoch == 0) %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
  gather(map_str, reward, -c(run, run_type, named_run_type, epoch), -starts_with("is_")) %>%
  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
  mutate(is_new = check_if_new_game(run_type, source) | check_if_new_game(run_type, target),
         is_new = factor(is_new, labels=c("Trained", "Held out")),
         named_meta_task = name_meta_task(meta_task))
```

@@

lang_meta_d = lang_meta_d %>%
  filter(epoch == 0) %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
  gather(map_str, reward, -c(run, run_type, named_run_type, epoch), -starts_with("is_")) %>%
  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
  mutate(is_new = check_if_new_game(run_type, source) | check_if_new_game(run_type, target),
         is_new = factor(is_new, labels=c("Trained", "Held out")),
         named_meta_task=name_meta_task(meta_task))
```

@@

```{r}
avg_lang_meta_d %>%
  filter(run_type %in% c("meta_batch_128", "language_simplified_random_holdout"),
         meta_task != "toggle_suits_rule") %>%
  select(-meta_task, -run_type) %>%
  mutate(is_new=as.character(is_new)) %>%
  mutate_at(vars(average_reward, contains("CI")), function(x) {round(x, digits=3)}) %>%
  stargazer(summary = F, rownames = F, digits=2)
```
# embeddings
```{r}
library(tsne)
```

>>>>

  p = ggplot(data, aes_string(x=x_var, y=y_var, color=color_var)) +  
    geom_hline(yintercept=0., linetype=2, alpha=0.5) +
    geom_point(stat="summary", fun.y=mean, size=2) +
    scale_color_manual(values=c("#555093", "#f38f22", "#88e1e1", "#008822"))

@@

```{r}
summary_plot(language_d %>%
               filter(epoch == 0, run_type == "meta_batch_128"),
             "named_game_type", "reward", "is_new_game",
             optimal_baselines) +
  facet_wrap(. ~ named_run_type) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#ggsave("writing/figures/language_basic.png", width=5, height=3.5)
#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/crappy_language.png", width=5, height=3)
```

@@

meta_d = meta_d %>%
  filter(epoch == 0) %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
  gather(map_str, reward, -c(run, run_type, named_run_type, epoch), -starts_with("is_")) %>%
  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
  mutate(is_new_source = check_if_new_game(run_type, source),
         is_new_target = check_if_new_game(run_type, target),
         is_new =  is_new_source | is_new_target,
         is_new = factor(is_new, labels=c("Trained", "Held out")),
         named_meta_task = name_meta_task(meta_task))
```

@@

lang_meta_d = lang_meta_d %>%
  filter(epoch == 0) %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
  gather(map_str, reward, -c(run, run_type, named_run_type, epoch), -starts_with("is_")) %>%
  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
  mutate(is_new_source = check_if_new_game(run_type, source),
         is_new_target = check_if_new_game(run_type, target),
         is_new =  is_new_source | is_new_target,
         is_new = factor(is_new, labels=c("Trained", "Held out")),
         named_meta_task=name_meta_task(meta_task))
```

@@

```{r}
avg_lang_meta_d %>%
  filter(run_type %in% c("meta_batch_128", "language_simplified_random_holdout"),
         meta_task != "toggle_suits_rule") %>%
  select(-meta_task, -run_type) %>%
  mutate(is_new=as.character(is_new)) %>%
  mutate_at(vars(average_reward, contains("CI")), function(x) {round(x, digits=3)}) %>%
  stargazer(summary = F, rownames = F, digits=2)
```

# Comparing different ways of performing a new task: from examples, from language, or from meta-mappings

```{r}
summary_plot(bind_rows(lang_meta_d %>%
                         filter(epoch == 0,
                                is_new_target & !is_new_source,
                                meta_task == "toggle_losers",
                                run_type == "meta_batch_128") %>%
                         mutate(result_type = "Meta-mapping old task (language cue)") %>%
                         select(result_type, target, run, reward) %>%
                         rename(game_str=target),
                       reward_d %>%                         
                         filter(epoch == 0,
                                is_new_game != "Trained",
                                run_type == "basic") %>%
                         mutate(result_type = "Examples of new task") %>%
                         select(result_type, game_str, run, reward),
                       language_d %>%                         
                         filter(epoch == 0,
                                is_new_game != "Trained",
                                run_type == "meta_batch_128") %>%
                         mutate(result_type = "Language directly") %>%
                         select(result_type, game_str, run, reward),
                       meta_d %>%
                         filter(epoch == 0,
                                is_new_target & !is_new_source,
                                meta_task =="toggle_losers",
                                run_type == "meta_batch_128") %>%
                         mutate(result_type = "Meta-mapping old task (example cue)") %>%
                         select(result_type, target, run, reward) %>%
                         rename(game_str=target)) %>%
               mutate(named_run_type = "Targeted 10% holdout",
                      result_type=str_wrap(result_type, width=20),
                      result_type=factor(result_type, levels=sort(unique(result_type))[c(1,3,4,2)])), # ugh
             "result_type", "reward", "result_type") +
  guides(color=F) +
  labs(x="Performing from ...", y="Average reward on held-out tasks")

#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/language_meta.png", width=7, height=3.5)
ggsave("writing/figures/why_meta_mapping.png", width=6, height=3)

# embeddings
```{r}
library(tsne)
```
